An inside-outside algorithms for mutant RNAs with applications to error detections in structured RNAs

### 2012-10-06 Recomb/introduction_RECOMB.tex
intro

@@

In recent years, studies as the \emph{Human Microbiome Project}~\cite{Turnbaugh2007}, 
leveraging the NGS techniques to sequence as many new organisms 
as possible, are producing a wealth of new information. Although
those techniques have a huge throughput, they yield a sequencing error rate of around
$4\%$~\cite{Huse2007}. This error can be highly reduced  when highly 
redundant multiple sequence allignments 
 are available, but in studies of new or not well known organisms, there is not
 enough  similarity to differentiate between the sequencing errors and the natural 
 polymorphisms that we want to observe, often inflating the diversity estimates~\cite{Kunin2010}.
  In rRNAs, on top of multiple sequence alignments, we have as additional 
 information the conserved secondary structure, and we want to use it to identify
highly probable sequencing errors. 
Given a new rRNA sequence, a first challenge to find the sequencing errors
  is to  efficiently explore the mutant space, 
which grows exponentially, guiding ourselves with the alignment and the consensus structure.

>>>>

In recent years, studies as the \emph{Human Microbiome Project}~\cite{Turnbaugh2007}, 
leveraging the NGS techniques to sequence as many new organisms 
as possible, are producing a wealth of new information. Although
those techniques have a huge throughput, they yield a sequencing error rate of around
$4\%$~\cite{Huse2007}. This error can be highly reduced  when highly 
redundant multiple sequence alignments 
 are available, but in studies of new or not well known organisms, there is not
 enough  similarity to differentiate between the sequencing errors and the natural 
 polymorphisms that we want to observe, often inflating the diversity estimates~\cite{Kunin2010}.

@@

In this paper, we tackle the problem of exploring an rRNA sequence mutant space, to
identify positions which are probably sequencing error, given the  rRNA family sequences
and its consensus structure.
